Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-02 EconGrowth.Rnw
More code cleanup prior to making graphs for CD with energy.

<<cobb-douglas, echo=FALSE>>=
####################
# Returns an nls Cobb-Douglas model for the country specified
##
cobbDouglasModel <- function(countryName){
  # Load the data that we need.
  dataTable <- loadData(countryName)

  # Establish guess values for alpha and lambda.
  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.3 # a typical value for alpha, the coefficient on capital stock

  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
#                 algorithm = "port",
                 start = list(lambda=lambdaGuess, alpha=alphaGuess),
#                 lower = list(lambda=-Inf, alpha=0),
#                 upper = list(lambda=Inf, alpha=1),
                 data=dataTable)
  return(modelCD)
}

>>>>

<<cobb-douglas, echo=FALSE>>=
####################
# Returns an nls Cobb-Douglas model for the country specified
##
cobbDouglasModel <- function(countryName){
  dataTable <- loadData(countryName) #Load the data that we need.
  # Establish guess values for alpha and lambda.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.7 #0.7 gives good results for all countries.
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
                 data=dataTable, 
                 start = list(lambda=lambdaGuess, alpha=alphaGuess),
                 algorithm = "port",
                 lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
                 upper = list(lambda=Inf, alpha=1)
                 )
  return(modelCD)
}
